\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[a4paper, total={6in, 10in}]{geometry}
% \title{Soumye Singhal}
\begin{document}
% \maketitle
    \centerline{\Huge{\textbf{SOUMYE SINGHAL}}}
    \begin{center}
    \textup{
        SOPHOMORE {\large\textperiodcentered} COMPUTER SCIENCE AND ENGINEERING, IITK\\
    }
    soumye@iitk.ac.in {\large\textperiodcentered} (+91)7054122337 {\large\textperiodcentered} http://github.com/soumye
    \end{center}


\begin{table}[h]
\section*{EDUCATION}
    \begin{tabular}{ |c|c|c|c| } 
        \hline
        Year & Degree & Institue & CGPA/Percentage \\ 
        \hline
        2015-19 & BTech CSE & Indian Institue of Technology, Kanpur & 9.8\\ 
        2015 & 12th $|$ CBSE & Bal Bharati Public School Pitampura, Delhi & 95.4\%\\ 
        2013 & 10th $|$ CBSE & Bal Bharati Public School Pitampura, Delhi & 10.0\\        
        \hline
    \end{tabular}
\end{table}

\section*{HONORS AND AWARDS}
\begin{itemize}
    \itemsep0em
    \item All India Rank 579 , JEE ADVANCED \hfill 2015
    \item 0.1 Percentile , JEE MAINS \hfill 2015
    \item KVPY Fellow $|$ All India Rank 272 , IISc Bangalore and Government of India \hfill 2013
    \item All India Top 30 , Group Mathematics Olympiad $|$ CBSE \hfill 2013
    \item JSTSE Scholarship Awardee , Government of Delhi   \hfill 2012 
    \end{itemize}
\section*{PROJECTS}
    \subsection*{Autonomous Underwater Vehicle (AUV)}
    {Member, Team AUV-IITK, Prof. K.S. Venkatesh \& Prof. Sachin Shinde \hfill IITK}
    \begin{itemize}
        \itemsep0em
        \item {Part of the team that built our institue's first AUV. }
        \item {Were placed 2nd at the national level competion SAVe, organized by NIOT Chennai.}
        \item {The aim of the Robot is detecting and following a line, hitting a buoy, firing torpedoes at given targets and dropping objects underwater.}
        \item {Used Robot Operating System (ROS) for Controls and OpenCV for Image Processing.} 
    \end{itemize}
    
    \subsection*{GymkhanaLive: NEWS Webapp}
    {Summer Project, Programming Club \hfill IITK}
    \begin{itemize}
        \itemsep0em
        \item Programmed a News Web Application using Django for the use of the campus community akin to twitter/quora.
    	\item The website displays the news and events of the various clubs and groups on campus.
    	\item Implemented features like login, search, like and comment.
    \end{itemize}
    
    \subsection*{Diophantine Equation}
    {Course Project, Prof. Nitin Saxena \hfill IITK}
    \begin{itemize} 
        \itemsep0em
        \item Read about various methods to solve Diophantine Equation.
        \item Gave a presentation on the project also.
    \end{itemize}
    
    \subsection*{System Security}
    {Course Project, Prof. Sandeep Shukla \hfill IITK}
    \begin{itemize} 
        \itemsep0em
        \item Exploited various vulnerabilites like BufferOverflow, Format string in Zoobar Sever's code.
        \item Fixed bug in the code to prevent attacks.
    \end{itemize}
\begin{table}[h]
\section*{SKILLS}
    \begin{tabular}{|r|l|}
        \hline
         Programming & C/C++, Python, X86 , MIPS, ROS, OpenCV, Octave, R \\
         \hline
         Web & Django, JavaScript, HTML, CSS \\ 
         \hline
         Utilities & Bash, Git, GDB, \LaTeX, Sublime, Vim \\
         \hline
         Platforms &  Windows, Linux(Ubuntu), Arduino, Android \\
        \hline
    \end{tabular}
\end{table}


\section*{RELEVANT COURSES}
\begin{tabular}{l l l}
\textbf{Completed}\\
 Introduction to Programming** & Partial Differential Equation & Linear Algebra**\\ 
 Introduction to Electrodynamics & Multivariable Calculus* & Abstract Algebra\\
 Introduction to Classical Mechanics & Discrete Mathematics & Thermodynamics\\
 Introduction to Electronics & Logic in Computer Science\\
\textbf{Ongoing}\\
 Data Structures and Algorithms & Probability and Statistics & Computer Organization\\
 Computer System Security & Computer Laboratory & Introduction to Economics\\

 {\footnotesize \ *  : A* Grade for exceptional performance}\\
 {\footnotesize ** : Batch Highest}
 \end{tabular}
 
 \section*{POSITIONS}
    \subsection*{Secretary, Programming club  IITK}
        \begin{itemize}
            \itemsep0em
            \item {Helped organize Linux Installation Drive, Freshers Proramming Contest and other activites.}
            \item {Helped in the functioning of the club by organizing contests and lectures on various topics.}
        \end{itemize}
        
    \subsection*{Secretary, Science Coffee House}
        \begin{itemize}
            \itemsep0em
            \item Part of a Hobby Group that regularly meets to discuss various scientific topics.
        \end{itemize}
    
    \subsection*{Project Mentor, ACA IITK}
        \begin{itemize}
            \itemsep0em
            \item Mentoring 6 students on a project on System and Cyber Security.
        \end{itemize}
 
 \section*{MISCELLANEOUS}
    \begin{itemize}
        \itemsep0em
        \item Google Devfest $|$ Made a weather and sports application for Android. 
        \item Electromania $|$ Made an Egg-Basket game using Digital IC’s and logic gates.
    \end{itemize}

\end{document}
